For Online Publication \\ Appendix for ``The Size Distribution of Firms and Industrial Water Pollution: A Quantitative Analysis of China''

### 2019-09-23 Documentation/DataAppendix_AEJ_Final.tex
appendix proofread

For an official introduction to the NGSPS and declassified information at the aggregated level, interested readers could refer to the book \textit{Data Collection of the National General Survey of Pollution Sources} (\begin{CJK}{GBK}{kai}《污染源普查数据集》, 中国环境科学出版社, 2011\end{CJK}), which is publicly available.

@@

The NGSPS was a joint effort of multiple national ministries in China. The survey was organized directly by the State Council with data collection and quality control done by specially trained field staffs. According to the Regulation on National General Survey of Pollution Sources [Decree of the State Council of the People's Republic of China (No. 508)], faking data would lead to financial penalties or even lawsuits. The purpose of the NGSPS is to understand the number of pollution sources and their distribution in different industries and regions; to understand the generation, discharge and treatment of major pollutants; to establish records for key pollution sources; to build a pollution source information database and an environmental statistics platform; and to provide basis for formulating policies and plans for economic and social development and environmental protection. The term ``pollution source'' here refers to premises, facilities and equipment which discharge pollutants to environment in the process of production, living or other activities or have adverse impact on environment, as well as other sources that result in pollution.

The survey covers all of the pollution units from agricultural, industrial, domestic sources, and facilities for the centralized treatment of pollution within the borders of the People's Republic of China. In this study, we focus on the {industrial pollution sources}, which consist of businesses from 39 manufacturing industries according to the \textit{Industrial Classification for National Economic Activities} (GB/T4547-2002).

@@

\textit{Key and Regular Sources.---}The firms in the industrial sources are divided into two groups, \textit{key sources} and \textit{regular sources}. A key source firm is required to file questionnaires that are more detailed than those filed by the regular source firms. A firm is categorized as a key source, if one of the following condition is satisfied:
\begin{enumerate}
    \item
    All production entities that discharge pollutants that contain heavy metal, hazardous waste, and radioactive substance.
    \item
    All production entities that belong to the 11 heavily polluting industries, which include: Paper and Paper Products; Food Processing; Raw Chemical Materials and Chemical Products; Textile; Ferrous Metal Smelting and Rolling Processing; Food Manufacturing; Production and Supply of Electric and Heating Power; Manufacturing of Leather, Fur, and Feather; Processing of Petroleum, Coking, and Nuclear Fuel; Manufacturing of Non-metallic Mineral Goods; Ferrous Metal Smelting and Rolling Processing.
    \item
    Firms with more than CNY 5 million in revenue that belong to the 16 key industries, which include: Beverage Manufacturing; Medicine Manufacturing; Chemical Fibers Manufacturing; Transportation Equipment Manufacturing; Coal Mining and Washing; Non-ferrous Metal Mining; Processing of Timber, and Manufacture of Wood, Bamboo, Rattan, Palm and Straw Products; Petroleum and Natural Gas Exploitation; General Purpose Machinery Manufacturing; Ferrous Metal Mining; Non-metal Mining; Apparel, Footwear and Caps Manufacturing; Water Production and Supply; Metal Products Manufacturing; Special Purpose Machinery Manufacturing; Communication Equipment, Computers and Other Electronic Equipment.
\end{enumerate}
A firm is categorized as a regular source firm, if none of the above conditions holds.

\textit{Variables.---}The survey collects information on the following variables for the industrial sources.
\begin{enumerate}
    \item
    Firm's basic registration information, geographic latitude and longitude, the receiving water body of firm's discharged wastewater, etc.
    \item
    The consumption of raw and intermediate inputs, including: water consumption, energy consumption (coal, petroleum, gas, electricity, etc.), the sulfur content of fuel, the consumption of hazardous intermediate input, etc.
    \item
    The quantity of each of the products produced by the firm.
    \item
    The type, size and number of the pollutants treatment equipment that the firms own.
    \item
    The generation, abatement, discharge and comprehensive utilization of various types of pollutants; and the operation of various kinds of pollution prevention and control facilities.
    \item
    The monitoring of pollutants emissions, including: the date and frequency of the monitoring; the type, quantity, and concentration of the pollutant.
\end{enumerate}

\textit{Pollutants.---}The pollutants included for the industrial sources are those that have general implications on pollution control. In particular, these pollutants are as follows.
\begin{enumerate}
    \item
    Wastewater: Chemical Oxygen Demand (COD), Ammonian, Petrochemicals, Volatile Phenols, Mercury, Cadmium, Plumbum, Arsenium, Hexavalent Chromium, Cyanidium. For Paper and Paper Product, Food Processing, Food Manufacturing and Beverage Manufacturing Industries, Five-days Biochemical Oxygen Demand ($\text{BOD}_5$) is added. For Urban Sewage Treatment Plants, Total Phosphorus, Total Nitrogen, and $\text{BOD}_5$ are added.
    \item
    Exhaust: Soot, Industrial Dust, Sulfur Dioxide. For Electrolytic Aluminium, Cement, Ceramic, Frosted Glass industries, Fluoride is added. For Vehicle Exhaust Census, Carbon Monoxide and Hydrocarbon are added.
    \item
    Industrial Solid Waste: Hazardous Waste (according to the \textit{National Catalogue of Hazardous Wastes}), Smelting Waste, Flying-Ash, Slag, Coal Refuse, Gangue, Radioactive Slag.
    \item
    Plaster discharged by Desulfurization Facilities, Sludge generated by waste water treatment facilities, and the remaining from burning hazardous waste.
    \item
    Radioactive pollution sources from the utilization of Concomitant Radioactive Mineral and from Civil Nuclear Power Generation.
\end{enumerate}

@@

There are three different methods to measure the level of pollutant emissions, which are \textit{Monitoring Method, Method of Emission Coefficient}, and \textit{Material Balance Method}. In this section, we describe these three methods and explain which method is used to determine the level of pollutant emissions in practice.

@@

\textit{Monitoring Method.---}In this method, the actual quantity and concentration of pollutants are measured, which are used to infer the annual quantity of the generation and discharge of different pollutants. In practice, there are three sources from which the monitored data are obtained, ranked by the priority of adoption when data from multiple sources are available: \textit{NGSPS monitoring, historical monitoring}, and \textit{online monitoring}. The NGSPS monitoring data are collected by the field staff in the survey year (2007). The historical monitoring data are measured and recorded in the past three years, with the latest data having the highest priority.\footnote{There are four different sources of historical data, ranked again by the priority of adoption when data from multiple sources are available: the historical data monitored by the local environmental authorities, the data monitored upon the completion of a newly constructed project, the data monitored by a third-party agency, and those self-reported by the firms.} The online monitoring data are those automatically uploaded by computerized and Internet-connected pollutants treatment equipment. Before the historical and online monitoring data are adopted, the field staff of the survey would ensure that the production condition and pollutant treatment technology have not undergone substantial changes.

@@

A pollution source needs to report monitored data, if any of the following four criteria is met:
\begin{enumerate}
    \item
    Nationally Monitored Key Pollution Sources {\begin{CJK}{GBK}{kai}(国控重点污染源)\end{CJK}}: all firms listed in the \textit{List of National Intensively Monitored Firms} {\begin{CJK}{GBK}{kai}(国家重点监控企业名单,环办函[2007]93号)\end{CJK}}.
    \item
    Facilities for Centralized Treatment of Pollution.
    \item
    Provincially Monitored Key Pollution Sources {\begin{CJK}{GBK}{kai}(省控重点污染源)\end{CJK}} that in sum account for 65\% of total provincial emission as is recorded in the \textit{2005 Environmental Statistic Yearbook}. That is for each of the major pollutants, starting from the most polluting firm and adding up the quantity of emission, all firms until the summation reaches the 65\% of the total provincial emission are recorded. The collection of the list of firms for all major pollutants provides the firms in this category.
    \item
    Newly established projects since 2005 whose pollutants discharge is higher than the least polluting firms in the Provincial Monitored Key Pollution Sources.
\end{enumerate}
These firms are later referred to as the \textit{monitored firms} in this document.

Starting from 2007Q1, for all Nationally Monitored Key Pollution Sources, Centralized Treatment Facilities, and Provincially Monitored Key Pollution Sources, waste water sources have to be monitored at least once per quarter, and exhaust sources have to be monitored at least once per six months.

The actual monitoring practice is subject to the following guidelines:
\begin{enumerate}
    \item
    The monitoring of Mercury, Cadmium, Hexavalent Chromium, Plumbum, and Arsenium must be conducted at the discharging outlets of individual factory workshops, with each outlets monitored separately.
    \item
    Other water-based pollutants are monitored at the outlets of the factory.
    \item
    The flow rates of wastewater and exhaust are monitored at the same time with the monitoring of pollutants discharges.
    \item
    The monitoring of pollution sources are conducted at the representative production and polluting time periods.
    \item
    All monitoring technical standards of wastewater pollutants follow \textit{The Technical Specifications Requirements for the Monitoring of Surface Water and Wastewater} {\begin{CJK}{GBK}{kai}(地表水和污水监测技术规范, HJ/T91-2002)\end{CJK}} and \textit{The Technical Specifications Requirements for the Monitoring of Wastewater Pollutants Emission} {\begin{CJK}{GBK}{kai}(水污染物排放总量监测技术规范, HJ/T92-2002)\end{CJK}}.
    \item
    For unstable wastewater sources, the samples are collected using the \textit{Water Ratio Automatic Sampler}.
    \item
    All monitoring technical standards of exhaust pollutants follow \textit{The Determination of Particulates and Sampling Methods of Gaseous Pollutants from Exhaust Gas of Stationary Sources} {\begin{CJK}{GBK}{kai}(固定污染源排气中颗粒物测定和气态污染物采样方法, GB/T16157-1996)\end{CJK}}.
\end{enumerate}

\textit{Method of Emission Coefficient.---}In this method, the generation and discharge of pollutants are calculated according to the \textit{Handbook of Emission Coefficient}, edited by the \textit{Chinese Academy of Sciences}. The benchmark coefficients are estimated based on firm's production technology, production scale, etc. The actual coefficients used are modified from the benchmark coefficients according to firm's use of intermediate inputs, its managerial practice, and the pollution treatment equipment installed. The actual pollutants generation and discharge are then calculated according to the actual production scale of the firm in year 2007.

\textit{Material Balance Method.---}In this method, the quantities of the materials entering and leaving a system are measured, and therefore the material flows which might have been unknown or difficult to measure without this method are identified. The exact rule of conservation used in the analysis of the system depends on the specific context, but all rules revolve around mass conservation, i.e., that matter cannot disappear or be created spontaneously. In parctice, a firm's usage of intermediate inputs, energy consumption, water consumption, and production technology are used simultaneously, in order that the calculated pollutants generation and discharge can realistically reflect the actual production and emission of the firm in reality.
%\textit{Material Balance Method.---}The Material Balance Method is an application of conservation of mass to the analysis of physical systems. By accounting for material entering and leaving a system, mass flows can be identified which might have been unknown, or difficult to measure without this technique. The exact conservation law used in the analysis of the system depends on the context of the problem, but all revolve around mass conservation, i.e. that matter cannot disappear or be created spontaneously. When applied, a firm's usage of intermediate inputs, energy consumption, water consumption, and production technology are considered simultaneously, in order that the calculated pollutants generation and discharge can realistically reflect the actual production and emission of the firm in reality.

\textit{Which Method Will Be Used in Practice?---}To determine which measurement method will be used in practice, the survey follows the following guidelines.
\begin{enumerate}
    \item
    The data of the Key Pollution Sources are obtained mainly through monitoring and the method of emission coefficient, while the material balance method is only used when the other two methods are not feasible. More specifically, the data of all firms that are identified as the monitored firms are obtained by monitoring. The data of other firms in the key sources are obtained by the method of emission coefficient.
    \item
    The data of the Regular Pollution Sources are obtained mainly through the method of emission coefficient, while the material balance method is used only when the method of emission coefficient is not feasible.
    \item
    Before being accepted, the monitored data are compared with those calculated from the method of emission coefficient. If the discrepancy is less than 20\% of the monitored value, the monitored value is used. If the discrepancy is larger than 20\%, the production technology and operating status of the firm are examined. If the operating status is in compliance with that specified in the technical regulations of the monitoring practice (for example, the firm has to reach at least 75\% of its production capacity when the emission is monitored), the monitored data are accepted. Otherwise, the emissions are calculated using the method of emission coefficient.
\end{enumerate}

\section{A Comparison of Firm Size Distributions for Different Samples}
%\section{Firm Size Distribution in NGSPS and CNEC}
This section compares the firm size distributions for different samples of firms in China. In Figure \ref{fig:distcomp}, we present the kernel densities of firm size estimated using different samples in NGSPS and CNEC.
%This section shows the firm size distributions by output value from the NGSPS and CNEC. In Figure \ref{fig:distcomp}, we present kernel densities of firm sizes estimated using different samples in NGSPS and CNEC.
\begin{figure}[t]
    \begin{center}
    \includegraphics[width=0.4\textwidth]{./Figures/ngsps_den_key_appen.pdf}%
    \includegraphics[width=0.4\textwidth]{./Figures/ngsps_den_all_appen.pdf} \\
    \includegraphics[width=0.4\textwidth]{./Figures/cnec_den_large_appen.pdf}
    \includegraphics[width=0.4\textwidth]{./Figures/cnec_den_all_appen.pdf}
    \caption{Firm Size Distributions in Various Data Sources}
    \floatfoot{Sources: NGSPS and CNEC. In all panels, the horizontal axes are in log-scale.}
    \label{fig:distcomp}
    \end{center}
\end{figure}
On the upper panels, we plot the firm size distributions for the samples that consist of the key source firms (the left panel) and all firms (the right panel) in the NGSPS, respectively. On the lower panels, we plot the firm size distributions for the \textit{Annual Surveys of Industrial Firms (ASIF)} sample (the left panel), which consists of all state-owned firms and private firms with sales above CNY 5 million, and the sample of all firms (the right panel) in the CNEC. There are two findings that we would like to emphasize:
%On the upper panel, we plot the firm size distribution by using only the key firms (left) and all firms (right) in NGSPS. On the lower panel, we plot those estimated using only the Annual Survey samples (left) and all firms (right). There are two findings that we would like to emphasize.
\begin{enumerate}
    \item
    Although the key source firms are on average larger than the firms in the full sample, they include both small and large firms, and the empirical density of the log output of the key source firms resembles a bell shape. This suggests that the key source firms are reflecting the characteristics of the firms over the entire range of firm size. As a result, no systematic bias will be introduced when we use the key source firms to empirically analyze the relationship between pollution intensity/treatment technology adoption and firm size in Section \rom{1}.B.
    %The key firms in NGSPS cover broadly firms of all sizes. Though the key firms tend to be larger than an average firm from the full sample, a fair amount of small firms are included. Hence both densities from the key and all firms resemble those bell-shaped densities from the normal distribution family. This also suggests that the estimated elasticity in Regression (1) of the main text is likely to reflect the correlation between production and emissions over the entire range of firm size.
    \item
    There are marked differences in the firm size distributions between the ASIF sample and CNEC full sample, with the ASIF sample missing most of the small firms. As a result, while the ASIF data are widely used in the studies of Chinese economy, we use the CNEC full sample in our paper, because both the small and large firms play a critical role in our empirical and quantitative analysis.
   % The densities estimated from the CNEC full sample and the Annual Surveys of Industrial Production subsample show marked difference, with the Annual Survey samples missing all the small firms, of which a lot are covered by the NGSPS key firms.
\end{enumerate}

In sum, the two take away points from the four panels in Figure \ref{fig:distcomp} are that the key firms in NGSPS are representative of both large and small firms, and that we have to use the CNEC full sample in companion with the NSGPS for our purpose.

@@

In this section, we present additional results on the statistical relationship between firm size and pollution intensity. In Section C.1, we show the scatter-plots and regression results for individual polluting industries and and for the whole manufacturing sector as well. In addition, we show that the negative relationship between firm size and pollution intensity holds conditional on whether the firms are using physical, chemical or biological technologies. We also show that our results in Section \rom{1}.B remain robust if we cluster the standard errors by provinces. In Section C.2, we explain our estimates on coefficients of the dummy variables, and compare our findings with those from the existing literature.

@@

The pollution intensity also exhibits rich provincial level variations. We take the regression results on the paper industry for example. Using Beijing as the benchmark, of all the remaining 29 provinces and municipalities, only the coefficient of Shanghai is negative and statistically insignificant. For the remainders, all estimates are positive and highly significant.\footnote{One province, Hebei is significant at 10\% level. Four others are significant at 1\% level while all others are significant at 0.1\% level. We notice here that Hebei, a province that is commonly considered as heavily affected by industrial pollution, is in fact an outlier, since the paper manufacturing is not its pillar industry.} The five most polluting provinces are Ningxia, Inner Mongolia, Gansu, Shaanxi and Xinjiang, for which the rankings of their provincial GDP in 2007 are respectively 29, 16, 27, 19 and 25 out of 31 provincial administrative regions (not including Hong Kong and Macau). Geographically, these are also inland provinces. In fact, despite that the majority of the paper manufacturers are located in Zhejiang and Guangdong (ranked 1st and 4th by GDP), the pollution level is lower comparing to those inland less developed regions. These patterns are highly robust across various specifications of our regressions. The general message we get from these dummy coefficients are the following. First, Beijing and Shanghai, arguably the political and economic center of China, exert pollution control standard far more stringent than the rest provinces. Second, inland and less developed provinces in general have worse control over and are more prone to the industrial pollution problem. These two patterns are broadly consistent with the environmental Kuznetz curve and the results from previous literature. However, unlike \citet{Jiangetal:2014}, ownership rights do not seem to have significant effects. If anything, the Foreign and Hong Kong, Macau and Taiwan based firms have only weakly better pollution controls. However, the statistical significance of the estimates never exceed 10\% across all our regressions. We conjecture that this could be because \citet{Jiangetal:2014}'s estimates are derived using a different sample of firms (in total 1,931 firms), while our data cover more firms.

@@

In this section, we provide some evidence in support of our modeling assumptions. In Section \ref{sec:distortions}, we present the evidence that motivates us to model the distortions as progressive taxes on output. In Section \ref{sec:appen_techspec}, we justify our choice of modeling the adoption of advanced treatment technology as fixed costs. We also describe additional distributional features of the treatment technology, including the {processing efficiency, designed processing capacity}, and {installation costs}, using the Paper and Paper Product industry as an example. Section \ref{sec:china_regulation} contains a brief summary of the environmental regulations in China.

@@

By using the first-order conditions, the firm level average product of capital $\phi_{k_i}$, labor $\phi_{l_i}$, and the capital/labor ratio $\kappa_i$ can be expressed as

@@

    \floatfoot{Source: CNEC. All panels are plot in log scale. Lines are least square fit. Data of the Paper and Paper Product Industry are plotted.}

>>>>

For an official introduction to the NGSPS and declassified information at the aggregate level, interested readers could refer to the book \textit{Data Collection of the National General Survey of Pollution Sources} (\begin{CJK}{GBK}{kai}《污染源普查数据集》, 中国环境科学出版社, 2011\end{CJK}), which is publicly available.

@@

The NGSPS was a joint effort of multiple national ministries in China. The survey was organized directly by the State Council with data collection and quality control done by specially trained field staff. According to the Regulation on National General Survey of Pollution Sources [Decree of the State Council of the People's Republic of China (No. 508)], faking data would lead to financial penalties or even lawsuits. The purpose of the NGSPS is to understand the total number of pollution sources and their distribution in different industries and regions; to understand the generation, discharge and treatment of major pollutants; to establish records for key pollution sources; to build a pollution source information database and an environmental statistics platform; and to provide basis for formulating policies and plans for economic and social development and environmental protection. The term ``pollution source'' here refers to premises, facilities and equipment which discharge pollutants to environment in the process of production, living or other activities or have adverse impact on environment, as well as other sources that result in pollution.

The survey covers all of the pollution units from agricultural, industrial, domestic sources, and facilities for centralized treatment of pollution within the borders of the People's Republic of China. In this study, we focus on the {industrial pollution sources}, which consist of businesses from 39 manufacturing industries according to the \textit{Industrial Classification for National Economic Activities} (GB/T4547-2002).

@@

\textit{Key and Regular Sources.---}Firms in the industrial sources are divided into two groups: \textit{key sources} and \textit{regular sources}. A key source firm is required to file questionnaires that are more detailed than those filed by the regular source firms. A firm is categorized as a key source, if one of the following conditions is satisfied:
\begin{enumerate}
    \item
    All production entities that discharge pollutants that contain heavy metal, hazardous waste, and radioactive substance.
    \item
    All production entities that belong to the 11 heavily polluting industries, which include: Paper and Paper Products; Food Processing; Raw Chemical Materials and Chemical Products; Textile; Ferrous Metal Smelting and Rolling Processing; Food Manufacturing; Production and Supply of Electric and Heating Power; Manufacturing of Leather, Fur, and Feather; Processing of Petroleum, Coking, and Nuclear Fuel; Manufacturing of Non-metallic Mineral Goods; Ferrous Metal Smelting and Rolling Processing.
    \item
    Firms with revenue of more than CNY 5 million in the 16 key industries, which include: Beverage Manufacturing; Medicine Manufacturing; Chemical Fibers Manufacturing; Transportation Equipment Manufacturing; Coal Mining and Washing; Non-ferrous Metal Mining; Processing of Timber, and Manufacture of Wood, Bamboo, Rattan, Palm and Straw Products; Petroleum and Natural Gas Exploitation; General Purpose Machinery Manufacturing; Ferrous Metal Mining; Non-metal Mining; Apparel, Footwear and Caps Manufacturing; Water Production and Supply; Metal Products Manufacturing; Special Purpose Machinery Manufacturing; Communication Equipment, Computers and Other Electronic Equipment.
\end{enumerate}
A firm is categorized as a regular source firm, if none of the above conditions holds.

\textit{Variables.---}The survey collects information on the following variables for the industrial sources.
\begin{enumerate}
    \item
    Firm's basic registration information, geographic latitude and longitude, the receiving water body wastewater discharged by the firm, etc.
    \item
    The consumption of raw and intermediate inputs, including: water, energy (coal, petroleum, gas, electricity, etc.), the sulfur content of fuel, hazardous intermediate input, etc.
    \item
    The quantity of each of the products produced by the firm.
    \item
    The type, size and number of the pollutants treatment equipment that the firms own.
    \item
    The generation, abatement, discharge and comprehensive utilization of various types of pollutants; and the operation of various kinds of pollution prevention and control facilities.
    \item
    The monitoring of pollutants emissions, including: the date and frequency of the monitoring; the type, quantity, and concentration of the pollutant.
\end{enumerate}

\textit{Pollutants.---}The pollutants included for the industrial sources are those that have general implications on pollution control. These pollutants are as follows.
\begin{enumerate}
    \item
    Wastewater: Chemical Oxygen Demand (COD), Ammonian, Petrochemicals, Volatile Phenols, Mercury, Cadmium, Plumbum, Arsenium, Hexavalent Chromium, Cyanidium. For Paper and Paper Product, Food Processing, Food Manufacturing and Beverage Manufacturing Industries, Five-days Biochemical Oxygen Demand ($\text{BOD}_5$) is added. For Urban Sewage Treatment Plants, Total Phosphorus, Total Nitrogen, and $\text{BOD}_5$ are added.
    \item
    Exhaust: Soot, Industrial Dust, Sulfur Dioxide. For Electrolytic Aluminium, Cement, Ceramic, Frosted Glass industries, Fluoride is added. For Vehicle Exhaust Census, Carbon Monoxide and Hydrocarbon are added.
    \item
    Industrial Solid Waste: Hazardous Waste (according to the \textit{National Catalogue of Hazardous Wastes}), Smelting Waste, Flying-Ash, Slag, Coal Refuse, Gangue, Radioactive Slag.
    \item
    Plaster discharged by Desulfurization Facilities, Sludge generated by waste water treatment facilities, and the remaining from burning hazardous waste.
    \item
    Radioactive pollution sources from the utilization of Concomitant Radioactive Mineral and from Civil Nuclear Power Generation.
\end{enumerate}

@@

Three different methods are used to measure the level of pollutant emissions: \textit{Monitoring Method, Method of Emission Coefficient}, and \textit{Material Balance Method}. In this section, we describe these three methods and explain which method is used to determine the level of pollutant emissions in practice.

@@

\textit{Monitoring Method.---}With this method, the actual quantity and concentration of pollutants are measured, which are used to infer the annual quantity of the generation and discharge of different pollutants. In practice, there are three sources from which the monitored data are obtained. Ranked by the priority of adoption when data from multiple sources are available, they are \textit{NGSPS monitoring, historical monitoring}, and \textit{online monitoring}. The NGSPS monitoring data are collected by the field staff in the survey year (2007). The historical monitoring data are measured and recorded in the past three years, with the latest data having the highest priority.\footnote{There are four different sources of historical data. Again, ranked by the priority of adoption when data from multiple sources are available, they are the historical data monitored by the local environmental authorities, the data monitored upon the completion of a newly constructed project, the data monitored by a third-party agency, and those self-reported by the firms.} The online monitoring data are those automatically uploaded by computerized and Internet-connected pollutants treatment equipment. Before the historical and online monitoring data are adopted, the field staff of the survey would ensure that the production condition and pollutant treatment technology have not undergone substantial changes.

@@

A pollution source is required to report monitored data, if any of the following four criteria is met:
\begin{enumerate}
    \item
    Nationally Monitored Key Pollution Sources {\begin{CJK}{GBK}{kai}(国控重点污染源)\end{CJK}}: all firms in the \textit{List of Nationally Monitored Key Pollution Sources} {\begin{CJK}{GBK}{kai}(国家重点监控企业名单,环办函[2007]93号)\end{CJK}}.
    \item
    Facilities for Centralized Treatment of Pollution.
    \item
    Provincially Monitored Key Pollution Sources {\begin{CJK}{GBK}{kai}(省控重点污染源)\end{CJK}} that in sum account for 65\% of total provincial emission as recorded in the \textit{2005 Environmental Statistic Yearbook}. That is for each of the major pollutants, starting from the most polluting firm and adding up the quantity of emission, all the firms until the summation reaches the 65\% of the total provincial emission recorded. The collection of the firms for all major pollutants makes the list.
    \item
    Newly established projects since 2005 whose pollutants discharge is higher than the least polluting firms in the Provincially Monitored Key Pollution Sources.
\end{enumerate}
These firms are later referred to as the \textit{monitored firms} in this document.

Starting from 2007Q1, for all Nationally Monitored Key Pollution Sources, Centralized Treatment Facilities and Provincially Monitored Key Pollution Sources, waste water sources have to be monitored at least once per quarter, and exhaust sources have to be monitored at least once per six months.

The actual monitoring practice is subject to the following guidelines:
\begin{enumerate}
    \item
    The monitoring of Mercury, Cadmium, Hexavalent Chromium, Plumbum, and Arsenium must be conducted at the discharging outlets of individual factory workshops, separately for each outlets.
    \item
    Other water-based pollutants are monitored at the outlets of the factory.
    \item
    The flow rates of wastewater and exhaust are monitored at the same time with the that of pollutants discharges.
    \item
    The monitoring of pollution sources are conducted at representative production and polluting time periods.
    \item
    All monitoring technical standards of wastewater pollutants follow \textit{The Technical Specifications for the Monitoring of Surface Water and Wastewater} {\begin{CJK}{GBK}{kai}(地表水和污水监测技术规范, HJ/T91-2002)\end{CJK}} and \textit{The Technical Specifications for the Monitoring of Wastewater Pollutants Emission} {\begin{CJK}{GBK}{kai}(水污染物排放总量监测技术规范, HJ/T92-2002)\end{CJK}}.
    \item
    For unstable wastewater sources, the samples are collected using the \textit{Water Ratio Automatic Sampler}.
    \item
    All monitoring technical standards of exhaust pollutants follow \textit{The Determination of Particulates and Sampling Methods of Gaseous Pollutants from Exhaust Gas of Stationary Sources} {\begin{CJK}{GBK}{kai}(固定污染源排气中颗粒物测定和气态污染物采样方法, GB/T16157-1996)\end{CJK}}.
\end{enumerate}

\textit{Method of Emission Coefficient.---}With this method, the generation and discharge of pollutants are calculated according to the \textit{Handbook of Emission Coefficient} edited by the \textit{Chinese Academy of Sciences}. The benchmark coefficients are estimated based on firm's production technology, production scale, etc. The actual coefficients used are modified from the benchmark coefficients according to firm's use of intermediate inputs, its managerial practice, and the pollution treatment equipment installed. The actual pollutants generation and discharge are then calculated according to the actual production scale of the firm in year 2007.

\textit{Material Balance Method.---}With this method, the quantities of the materials entering and leaving a system are measured. Therefore the material flows which might have been unknown or difficult to measure without this method are indirectly measured. The exact rule of conservation used in analyzing the system depends on specific context, but all rules revolve around mass conservation. In practice, a firm's usage of intermediate inputs, energy, water as well as production technology are considered simultaneously, in order that the calculated pollutants generation and discharge can realistically reflect the actual production and emission of the firm in reality.

\textit{Which Method Will Be Used in Practice?---}To determine which measurement method will be used in practice, the survey follows the following guidelines.
\begin{enumerate}
    \item
    The data of the Key Pollution Sources are obtained mainly through monitoring and the method of emission coefficient, while the material balance method is only used when the other two methods are not feasible. %More specifically, the data of all firms that are identified as the monitored firms are obtained by monitoring. The data of other firms in the key sources are obtained by the method of emission coefficient.
    \item
    The data of the Regular Pollution Sources are obtained mainly by the method of emission coefficient, while the material balance method is used only when the method of emission coefficient is not feasible.
    \item
    Before accepted, the monitored data are compared with those calculated from the method of emission coefficient. If the discrepancy is less than 20\% of the monitored value, the monitored value is used. If the discrepancy is larger than 20\%, the production technology and operating status of the firm are examined. If the operating status is in compliance with that specified in the technical regulations of the monitoring practice (for example, the firm has to reach at least 75\% of its production capacity when the emission is monitored), the monitored data are used. Otherwise, the emissions are calculated using the method of emission coefficient.
\end{enumerate}

\section{A Comparison of Firm Size Distributions for Different Samples}
%\section{Firm Size Distribution in NGSPS and CNEC}
This section compares the firm size distributions from the different samples. In Figure \ref{fig:distcomp}, we present the kernel densities of firm size estimated using different samples in NGSPS and CNEC.
%This section shows the firm size distributions by output value from the NGSPS and CNEC. In Figure \ref{fig:distcomp}, we present kernel densities of firm sizes estimated using different samples in NGSPS and CNEC.
\begin{figure}[t]
    \begin{center}
    \includegraphics[width=0.4\textwidth]{./Figures/ngsps_den_key_appen.pdf}%
    \includegraphics[width=0.4\textwidth]{./Figures/ngsps_den_all_appen.pdf} \\
    \includegraphics[width=0.4\textwidth]{./Figures/cnec_den_large_appen.pdf}
    \includegraphics[width=0.4\textwidth]{./Figures/cnec_den_all_appen.pdf}
    \caption{Firm Size Distributions in Various Data Sources}
    \floatfoot{Sources: NGSPS and CNEC. In all panels, the horizontal axes are in log-scale.}
    \label{fig:distcomp}
    \end{center}
\end{figure}
In the upper panels, we plot the firm size distributions of the key sources (the left panel) and all firms (the right panel) in the NGSPS respectively. In the lower panels, we plot those of the \textit{Annual Surveys of Industrial Firms (ASIF)} sample (the left panel), which consists of all state-owned firms and private firms with sales above CNY 5 million, and of all firms (the right panel) in the CNEC. There are two findings that we would like to emphasize:
%On the upper panel, we plot the firm size distribution by using only the key firms (left) and all firms (right) in NGSPS. On the lower panel, we plot those estimated using only the Annual Survey samples (left) and all firms (right). There are two findings that we would like to emphasize.
\begin{enumerate}
    \item
    Although the key source firms are indeed a bit larger on average, they include both small and large firms; and the empirical density of the log output of the key source firms resembles a bell shape. This suggests that the key source firms are reflecting the characteristics of the firms over the entire range of the firm size distribution. As a result, the systematic bias introduced when using the key source firms to empirically analyze the intensity/size relationship in Section \rom{1}.B would be limited.
    %The key firms in NGSPS cover broadly firms of all sizes. Though the key firms tend to be larger than an average firm from the full sample, a fair amount of small firms are included. Hence both densities from the key and all firms resemble those bell-shaped densities from the normal distribution family. This also suggests that the estimated elasticity in Regression (1) of the main text is likely to reflect the correlation between production and emissions over the entire range of firm size.
    \item
    There are marked differences in the firm size distributions between the ASIF sample and CNEC full sample, with the ASIF sample missing most of the small firms. As a result, while the ASIF data are widely used in studies of Chinese economy, we use the CNEC full sample in our paper, because both the small and large firms play a critical role in our empirical and quantitative analysis.
   % The densities estimated from the CNEC full sample and the Annual Surveys of Industrial Production subsample show marked difference, with the Annual Survey samples missing all the small firms, of which a lot are covered by the NGSPS key firms.
\end{enumerate}

In sum, the two take away points from the four panels in Figure \ref{fig:distcomp} are that the key firms in NGSPS are representative of both large and small firms; and that it is more appropriate to use the CNEC full sample in companion with the NSGPS for our purpose.

@@

In this section, we present additional results on the statistical relationship between firm size and pollution intensity. In Section C.1, we show the scatter-plots and regression results for individual polluting industry and for the whole manufacturing sector as well. In addition, we show that the negative relationship between firm size and pollution intensity continues to hold after conditioning on whether firms are using physical, chemical or biological technologies. We also show that our results in Section \rom{1}.B remain robust if we cluster the standard errors by province. In Section C.2, we provide a brief overview on our estimates on coefficients of the dummy variables, and compare our findings with those from the existing literature.

@@

The pollution intensity also exhibits rich provincial level variations. We take the regression results on the paper industry for illustration purpose. Using Beijing as the benchmark, of all the remaining 29 provinces and municipalities, only the coefficient of Shanghai is negative and statistically insignificant. For the remainder provinces, all estimates are positive and highly significant.\footnote{One province, Hebei is significant at 10\% level. We notice here that Hebei, a province that is commonly considered as heavily affected by industrial pollution, is in fact an outlier, since the paper manufacturing is not its pillar industry.} The five most polluting provinces are Ningxia, Inner Mongolia, Gansu, Shaanxi and Xinjiang, for which the respective provincial GDP ranking in 2007 are 29, 16, 27, 19 and 25 out of 31 provincial administrative regions (not including Hong Kong and Macau). Geographically, these are also inland provinces. In fact, despite that the majority of the paper manufacturers are located in Zhejiang and Guangdong (ranked 1st and 4th by GDP), their pollution levels are lower comparing to those inland less developed regions. These patterns are highly robust across various specifications of our regressions. The general message we get from these dummy coefficients are the following. First, Beijing and Shanghai, arguably the political and economic center of China, exert pollution control standard far more stringent than the rest provinces. Second, inland and less developed provinces in general have worse control over and hence are more prone to industrial pollution problem. These two patterns are broadly consistent with the environmental Kuznetz curve and results from previous literature. However, unlike \citet{Jiangetal:2014}, ownership rights do not seem to have significant effects. If anything, the Foreign and Hong Kong, Macau and Taiwan based firms have only weakly better pollution controls. However, the statistical significance of the estimates never exceed 10\% across all our regressions. We conjecture that this could be because \citet{Jiangetal:2014}'s estimates are derived using a different sample of firms (in total 1,931 firms), while our data cover more firms.

@@

In this section, we provide some evidence in support of our modeling assumptions. In Section \ref{sec:distortions}, we present the evidence that motivates us to model the distortions as progressive taxes on output. In Section \ref{sec:appen_techspec}, we justify our choice of modeling the adoption of advanced treatment technology as fixed costs. We also describe additional technical features of the treatment technology, including the {processing efficiency, designed processing capacity}, and {installation costs}, using the Paper and Paper Product industry as an example. Section \ref{sec:china_regulation} contains a brief summary of the environmental regulations in China.

@@

By using the first-order conditions, the firm-level average product of capital $\phi_{k_i}$, labor $\phi_{l_i}$ and the capital/labor ratio $\kappa_i$ can be expressed as

@@

    \floatfoot{Source: CNEC. All panels are plotted in log scale. Lines are least square fit. Data of the Paper and Paper Product Industry are plotted.}
